Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-13 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued II} Added..

\subsection{From Real-valued to Interval-valued}

@@

>>>>

\subsection{From Real-valued to Interval-valued I}

@@

\subsection{From Real-valued to Interval-valued II}

Since we cannot restrict our convex interval-valued function mapping
only finite number of intervals, let's consider another natural interval-valued
function. Before we consider them, we review the counterpart of Weight-convex,
Weight-concave\nb\cite{PecaricTong1992,Brzdek_2014}.

\begin{definition}A function\nb$c:\left[0,1\right]\rightarrow\left[0,1\right]$
is called Wright-concave if for any three numbers\nb$x_{0}$, $x_{1}$,
and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies $c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)$.\end{definition}

\begin{example}Given a concave function\nb$c:$ For any $\delta\ge0$,
there is an additive interval-valued function\nb$\iota_{\delta}':\left[0,1\right]\rightarrow\mathscr{I}_{\delta}'$
defined by\end{example}
